### 2024-10-20 src/Submission.Rnw
Added introduction, MLE review, and Likelihood estimate review

@@

# Plot residuals to check for patterns
plot(ddat$bmi, residuals, main = "Residuals vs BMI", xlab = "BMI", ylab = "Residuals")
@

@@

# Print the result
cat("Likelihood Ratio Test Statistic:", LRT_stat, "\n")
cat("p-value:", p_value, "\n")
@

>>>>

\section{Introduction}
The importance of understanding the diabetes dataset it to further our knowledge of what the key causes of diabetes are, and how they can be predicted. The dataset contains 11 variables, and the target variable is the progression of diabetes. The dataset contains 442 observations and 11 variables and we are understanding the factors involved which are:
\begin{itemize}
    \item \textbf age    - age in years
    \item \textbf sex    - male and female
    \item \textbf bmi    - body mass index
    \item \textbf bp     - average blood pressure
    \item \textbf s1     - TC: total serum cholesterol
    \item \textbf s2     - LDL: low-density lipoproteins
    \item \textbf s3     - HDL: high-density lipoproteins
    \item \textbf s4     - TCH: total cholesterol / HDL
    \item \textbf s5     - LTG: possibly log of serum triglycerides level
    \item \textbf s6     - GLU: blood sugar level
    \item \textbf target - measure of disease progression one year after baseline
\end{itemize}
Each of the feature variables have been mean centered and scaled by the standard deviation times the square root of the number of sample.

Our investigation is to look at the more commonly known variables that affect the progression of diabetes in the observations of this dataset. These are more specifically age and BMI. We will be using the maximum likelihood estimation method to estimate the parameters of the linear regression model for the progression of diabetes based on BMI, then using the model we will do a comparison study on how age combined with BMI affects the progression of diabetes compared to BMI alone.

We will compute 95\% confidence intervals for the parameters estimated in our MLE model using the likelihood interval obtained earlier. This will provide a range of plausible values for each parameter in the population, helping us understand the uncertainty in our estimates.

We will use the bootstrap method to construct confidence intervals for the correlation coefficient between blood pressure and diabetes progression. This non-parametric approach will allow us to make inferences about the strength of this relationship in the population without making strong distributional assumptions.

@@

# Plot residuals to check for patterns
plot(ddat$bmi, residuals, main = "Residuals vs BMI", xlab = "BMI", ylab = "Residuals")
@
\subsection*{MLE Data Analysis}
With the assumption that the data is of a normal distribution and follows linear regression beta0 = 21.86, indicates that this is your progression if your BMI was 0, this is unrealistic as no one has this, the slope being labelled beta1 = 0.31 indicates every BMI increment of 1 would increase progression by 0.31 showing a small positive association which is reasonable, and standard deviation being 4102.63 is unrealistically high implying that BMI alone is not enough to determine the progression of diabetes based on the model or there is outlier variance that is just not explained by BMI. This is reasonable given the data is 10 measured variables and you would assume that the other 9 are not all redundant and cannot be predicted by BMI alone even though there is some correlation.

@@

# Print the result
cat("Likelihood Ratio Test Statistic:", LRT_stat, "\n")
cat("p-value:", p_value, "\n")
@
\subsection*{Likelihood Ratio Test Analysis}
Given the p-value is such a small number being less than 0.05, it can be concluded that the model with BMI and age is a better fit than the model with BMI as the only constituent and the likelihood ratio test backs up this data and indicates a large improvement. This was almost assumed given the data in the set has 10 variables and would be poorly constructed if so many were redundant which concludes through testing and general reasoning that adding additional variables will contribute to the accuracy of the model.
